Investigating the Underprovision of Public Goods: Does Segregation Matter?

### 2020-05-01 draft_v_4_30.Rmd
finalization of aggr plots

rp_aggr <- rp_impute %>%
   select("biggestsplit", "biracial", "whiteideology_fill2", "medincinterp",
            "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "nonpartisan",
               "south", "midwest", "west")

@@

```{r fin_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016). The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data. The plot on the right shows the pattern of missingness among the variables. We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 6, fig.height = 5, fig.pos="H"}

@@

fin_imp_aggr <- fin_imp %>%
  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, 
         chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp,
         pctover65, pctcollegegradinterp)

@@

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1)

# this plot tells us that only .58% of the data are complete (not missing anything)

>>>>

rp_aggr <- rp_impute %>%
   select("biggestsplit", "biracial", "whiteideology_fill2", "medincinterp",
            "diversityinterp",
             "pctasianpopinterp", "pctblkpopinterp", "pctlatinopopinterp",
             "pctrentersinterp", "pctcollegegradinterp", "nonpartisan",
               "south", "midwest", "west") %>%
  rename("Racial Divide" = biggestsplit, "Biracial Contest" = biracial, 
         "White Ideology" = whiteideology_fill2, "Median HH Income" = medincinterp,
         "Diversity" = diversityinterp, "% Asian" = pctasianpopinterp, 
         "% Black" = pctblkpopinterp, "% Latino" = pctlatinopopinterp,
         "% Renters" = pctrentersinterp, "% College Grads" = pctcollegegradinterp,
         "Nonpartisan Elect." = nonpartisan, "South" = south, "Midwest" = midwest,
         "West" = "west")

@@

```{r fin_aggr_plot, echo = FALSE, fig.cap = "This plot examines the pattern of missing data in the the original financial segregation dataset from Trounstine (2016). The plot on the left shows the percentage of missing data for each variable with missing data and reveals that a large number of variables are missing the vast majority of data. The plot on the right shows the pattern of missingness among the variables. We can see that only .58\\% of observations are complete (have no missing values), and a large majority of the observations are missing data for many variables.", fig.width= 7, fig.height = 5, fig.pos="H"}

@@

fin_imp_aggr <- fin_imp %>%
  select(ideology_fill, H_citytract_NHW_i, chng5pctblk, chng5pctlatino, 
         chng5pctasian, diversityinterp, pctblkpopinterp, pctasianpopinterp,
         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp,
         pctover65, pctcollegegradinterp) %>%
    rename("White Ideology" = ideology_fill, "White/Non-White H Index" = H_citytract_NHW_i,
           "5Y Change % Black" = chng5pctblk, "5Y Change % Latino" = chng5pctlatino, 
           "5Y Change % Asian" = chng5pctasian, "Diversity" = diversityinterp, 
           "% Asian" = pctasianpopinterp, "% Black" = pctblkpopinterp, 
           "% Latino" = pctlatinopopinterp, "Median HH Income" = medinc_cpi,
           "% Local Gov. Worker" = pctlocalgovworker_100, "% Renters" = pctrentersinterp, 
           "% College Grads" = pctcollegegradinterp, "% 65+" = pctover65)

@@

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.4, gap=2, ylab=c("Proporiton of Missing Values","Combinations"), srt = 45)
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "", font.main = 1, font.axis = 1, cex.main = 1, line = 3,  oma = c(1,3,5,1), font.main = 1, font.axis = 1, srt = 45)
# this plot tells us that only .58% of the data are complete (not missing anything)
